### 2016-05-05 plosOneJordanousKeller/rebuttal.txt

PONE-D-16-09839
Creativity is what we say it is: identifying key components of creativity
PLOS ONE

We invite you to submit a revised version of the manuscript that addresses all concerns of the Reviewers. When doing this please indicate in your accompanying letter the exact places of the manuscript, which were changed as the response of the Reviewers’ remark. Please insert a change to the manuscript as a response of each concern. Please insert a section to the Discussion part of the revised manuscript even in case you disagree with any comment of the Reviewers noting the alternative view and the detailed reasons of your disagreement.

 ***** IF THERE ARE ANY POINTS WE WANT TO DISAGREE WITH, WE NEED TO PUT COMMENTARY ON THIS IN THE DISCUSSION OF THE PAPER  *****

We encourage you to submit your revision within forty-five days of the date of this decision. Please note that any manuscripts that require a revision period greater than 6 months should be resubmitted as a new submission to PLOS ONE. Any manuscripts remaining in Editorial Manager after 6 months will be withdrawn.

 ***** DATE OF DECISION 7 APRIL

When your files are ready, please submit your revision by logging on to http://pone.edmgr.com/ and following the Submissions Needing Revision link. Do not submit a revised manuscript as a new submission. Before uploading, you should proofread your manuscript very closely for mistakes and grammatical errors. Should your manuscript be accepted for publication, you may not have another chance to make corrections as we do not offer pre-publication proofs.

 ***** SEE ABOVE!!!  *****

In addition, when submitting your revision please include the following items:

* A rebuttal letter that responds to each point brought up by the academic editor and reviewer(s). This letter should be uploaded as a 'Response to Reviewers' file.
* A clean revised manuscript as your 'Manuscript' file.
* A marked-up copy of the changes made from the previous article file as a 'Revised Manuscript with Track Changes' file. This can be done using 'track changes' in programs such as MS Word and/or highlighting any changes in the new document.
***** WE'VE AGREED TO USE LATEX STRIKETHROUGH FOR REMOVED TEXT, AND BOLD FONT FOR ADDED TEXT *****

While revising your submission, we encourage you to use PACE (the Preflight* Analysis and Conversion Engine, http://pace.apexcovantage.com/), a digital diagnostic and conversion tool for figure files. PACE helps users ensure that their figures meet PLOS requirements and that the quality of published figures will be as high as possible.

***** ANNA TO LOOK AT THIS *****

To use PACE, you must first register as a user. Then, login and navigate to the UPLOAD tab, where you will find detailed instructions on how to use the tool. If you encounter any issues or have any questions when using PACE, please email us at figures@plos.org.

For more information on how to upload your revised submission, see our video: http://blogs.plos.org/everyone/2011/05/10/how-to-submit-your-revised-manuscript/

When submitting your revision, we need you to address these additional requirements.

Please ensure that your manuscript meets PLOS ONE's style requirements, including those for file naming. The PLOS ONE style templates can be found at

http://www.journals.plos.org/plosone/s/file?id=wjVg/PLOSOne_formatting_sample_main_body.pdf and http://www.journals.plos.org/plosone/s/file?id=ba62/PLOSOne_formatting_sample_title_authors_affiliations.pdf

***** For some reason, we've fallen foul of some of these, so I'll check that *****

1.  We request that you please report additional details in your Methods:
i) A detailed overview of the search strategy used to identify papers for the creativity corpus and non-creativity corpus
ii) The specific methods for selecting papers, including inclusion and exclusion criteria
In addition, please include a figure of a flow diagram describing your search strategy (see http://prisma-statement.org/PRISMAStatement/FlowDiagram.aspx for examples)
We appreciate your attention to these requests."

***** ANNA TO DO THIS *****

JW (Assoc Ed) 9 Mar 2016: **EO** At PRTC, please go back for crosscheck, do not ping with follow up. For crosscheck, please go back with "Thank you for submitting the above manuscript to PLOS ONE. During our internal evaluation of the manuscript, we found significant text overlap between your submission and the following previously published works, on which you are an author:

http://www.creativitypost.com/technology/technology/evaluating_computational_creativity
The re-use of text from a previous publication may have implications for the copyright or license that applies to the published article. To avoid any concerns in this respect, we would recommend that you revise the manuscript to either remove any text overlap where possible/appropriate, or to clearly indicate that the text reproduces information already reported in detail elsewhere (e.g. “As described in detail previously [ref],…”) citing the relevant sources.

  ***** BILL TO CHECK THIS OVERLAP WITH THE MENTIONED BLOG POST *****

2.

We note that you stated “data are available upon request” at submission. Could you please upload the minimal data set underlying the findings in your study in the manuscript, supplemental files, or in a stable public repository? If this is not the case, and your data are available upon request because of an ethical or legal restriction, or because you obtained data from a third party, please include the following in your revised cover letter:

 ***** BILL TO UPLOAD WORKING DATA SET TO SUSSEX REPOSITORY AND ADD LINK TO DataAvailabilityStatement.rtf FILE  *****

3. Please upload a copy of Figure1-6, to which you refer ithroughtout your manuscript. If the figure is no longer to be included as part of the submission please remove all reference to it within the text.

4. Please include a copy of Table 1 which you refer to in your text on page 11.

***** THESE WERE INCLUDED BUT NEEDED TO BE HIGHER RESOLUTION (SEE REVIEWER 2 COMMENTS) - ANNA TO REVISE FIGURES/TABLES  *****

Reviewer #1: This is interesting paper that could have some value in the literature on creativity and innovation. The conceptual framing of the paper did not work for me, but I see a path forward for the authors that would help clarify what they’re trying to do – and the implications that can be drawn from their results.

My major concerns about the paper are (a) the implied reification in the title, abstract, and introduction; and (b) that the authors aren’t really attempting to come up with a definition at all.

Implied reification. To say that creativity is subjective and difficult if not impossible to define would have been understandable 20 years ago, but this was a major weakness of the field and many scholars have tackled the issue. Several highly cited papers have focused the field on a general definition – interestingly, this paper cites most of them – and most creativity scholars consider this to be a minor issue in the field today. To frame a paper such as this one around the idea that the definition of creativity is subjective and still needs to be found is a bit odd, as it implies that creativity is a real thing that we have yet to discover adequately. But creativity doesn’t really exist; rather, it’s a label we made up to describe certain behaviors and outcomes. So “discovering” the definition feels weird to me. The authors can disagree with the definitions at hand, or revise them, or argue that we’ve been defining it incorrectly all this time – those would all be fair perspectives (e.g., Dean Keith Simonton makes these arguments regularly, and his analyses are moving the field forward). But to argue that we haven’t hit on the right definition yet? I’m not sure that’s a workable approach.

Is the point really a definition? I suspect it’s not. The resulting “definition” (Figures S5 and S6) doesn’t strike me as a definition at all. It’s a clever, unique approach to a model (or maybe even the beginnings of a theory) of creativity, essentially a meta-model along the lines of what Vartanian (2014) called for recently. But I know of no one – not a scholar, not a practitioner – who would provide such a “definition” when asked what creativity is. But if asked for a model on how creativity emerges, I think the authors’ proposed model is something they would share.

 ***** BILL TO DEAL WITH ABOVE POINTS AND REFRAMING  *****

In general, I found the methods to be well-explained and carefully done, but I have some experience using these methods (albeit limited), and other reviewers without such experience may request greater detail, which I would understand. But for me, they felt appropriate and offered a unique way to get at the components of creativity.

 ***** ANNA TO ADD MORE DETAIL ON METHODOLOGY FOR IDENTIFYING PAPERS AS REQUESTED BY EDITOR. 
       BILL TO CHECK TECHNICAL DETAIL OF METHODS AND SEE IF THEY ARE REPORTED IN AN APPROPRIATE LEVEL OF DETAIL  *****

I recommend reframing the paper as a meta-model or meta-theory employing previously unused methods. That gets to the heart of the matter much more directly (and accurately), and it speaks to the type of work Vartanian and others have been calling for as the field of creativity matures.

 ***** THIS FITS INTO THE WORK BILL IS DOING FOR THE ABOVE POINT  *****

Reference
Vartanian, O. (2014). Toward a cumulative psychological science of aesthetics, creativity, and the arts. Psychology of Aesthetics , Creativity , and the Arts, 8(1), 15-17.

 ***** LET'S BOTH READ THIS! BILL TO ADD SOME CONTENT RELATIVE TO THIS WHILE DEALING WITH REVIEWER 1's FIRST POINT *****

Reviewer #2: Review of “Creativity is what we say it is: identifying key components of creativity” for PLoS ONE

This paper proposes that creativity be defined in terms of themes emerging as a result of word clusters analysis of scholarly papers on creativity. I am not convinced that this approach captures the essence of what creativity is (any more than doing this kind of word cluster analysis of your own name on the internet would capture the essence of who you are).

***** BILL I'M SURE WE COULD ADD REFERENCES TO SUPPORT OUR APPROACH AGAINST THIS CRITICISM? ****

I am sympathetic with Gabora, O’Connor, & Ranjan’s (2012) conviction of that creativity needs to be defined in terms of internal change to the creator’s network of understandings. I am not altogether convinced by the authors’ that this kind of analysis makes creativity easier to evaluate. However, the approach is new and interesting and at the very least could provoke fruitful discussion of what is meant by creativity. Therefore I believe it could make a valuable contribution to the literature.

Literature Cited
Gabora, L., O’Connor, B., & Ranjan, A. (2012). The recognizability of individual creative styles within and across domains. Psychology of Aesthetics, Creativity, and the Arts, 6(4), 351-360.

 ***** ANNA TO CHECK HOW THE GABORA ET AL PAPER FITS INTO THIS
       (UNLESS THIS COMES UP IN THE WORK BILL IS DOING FOR REVIEWER 1'S MAIN POINT??) *****

A concern I have about the methodology concerns the set of papers used in the analysis, provided in Figure 1. (Note: this figure is rather hazy; in the final paper a higher resolution version should be used.) Despite the authors’ intention to capture how is creativity is understood from a broad range of vantage points and disciplines, almost all of these papers are in psychology journals. In my view they should have included papers from other scholarly journals that discuss creativity and innovation, e.g. design, architecture, art, theatre, film, multimedia, creative writing, electronic arts, and engineering journals.

 ***** ANNA TO ADD DIAGRAM REPRESENTING JOURNAL MAKE UP AND COMMENT ON THIS IN REBUTTAL/DISCUSSION OF PAPER  *****

I would suggest that the authors exaggerate the extent to which scholars differ in their view of what constitutes creativity (see p. 5). Completely unanimous agreement on anything in psychology is rare but it seems to me there is pretty unanimous agreement that creativity be defined in terms of (1) new/original and (2) useful/aesthetically appealing, or some variant of these. The authors’ approach still makes an interesting and provocative contribution even if there is widespread agreement on what creativity is.

 ***** ANNA TO ADD CONTENT ON HOW novelty/usefulness ARE NECESSARY BUT NOT SUFFICIENT, USING COMPUTATIONAL CREATIVITY SOFTWARE AND EXTRA COMMENTARY ON CREATIVITY = NOVELTY+USEFULNESS+???  *****

The paper is well-written overall, though there are some minor spelling / grammatical errors, e.g., “which” instead of “that on the first line of the abstract, and missed commas, e.g., after the word ‘sciences’ in the second paragraph.

 ***** WE'LL BOTH CATCH SOME OF THESE DURING PROOFREADING/EDITING/FINAL SPELL CHECK. BILL WOULD YOU MIND CHECKING THESE PARTICULAR TYPOS? *****

### 2016-05-19 plosOneJordanousKeller/PAPER/plos_JordanousKeller.tex
Changes from papeeria
Edits on method

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

@@

@@

The 30 papers selected for the creativity corpus are listed in Fig. 1. %\ref{S1_Fig}. 
The papers were carefully chosen so as to cover a wide range of years (1950-2009) and academic disciplines. A paper was included if it was considered particularly influential, as measured by the number of times it had been cited by other academic authors. For papers published in recent years and which have consequently not yet accrued many citations, selection was based on subjective judgement of influence.

>>>>

% ligatures disabled
\usepackage{microtype}
%\DisableLigatures[f]{encoding = *, family = * }

@@

% Use strikethrough for track changes 
\usepackage[normalem]{ulem}
% command is \sout{text text text etc}

@@

The 30 papers selected for the creativity corpus are listed in Fig. 1. %\ref{S1_Fig}.

i) A detailed overview of the search strategy used to identify papers for the creativity corpus and non-creativity corpus
ii) The specific methods for selecting papers, including inclusion and exclusion criteria

\textbf{Paper selection for the creativity corpus was governed by inclusion criteria based on measuring the influence of a paper and coverage of a wide range of years and academic disciplines: }
\begin{itemize}
\item \textbf{Papers must have, as their primary focus, discussion of the nature of creativity.}
\item \textbf{The primary inclusion criterion was to choose particularly influential papers, as measured by the number of times it had been cited by other academic authors. For papers published in recent years and which have consequently not yet accrued many citations, selection was based on subjective judgement of influence.}
\item \textbf{Cross section of years [the corpus was compiled in 2010] over the range of years 1950-2009. 1950 was chosen as a starting point in recognition of the effect of J. P. Guilford's presidential address to the American Psychological Association \cite{guilford50}, which examined contemporary creativity research (or more specifically, the lack of thereof). His talk was highly influential in encouraging more creativity research activity \cite{kaufman09}.}
\end{itemize}
\sout{The papers were carefully chosen so as to cover a wide range of years (1950-2009) and academic disciplines. A paper was included if it was considered particularly influential, as measured by the number of times it had been cited by other academic authors. For papers published in recent years and which have consequently not yet accrued many citations, selection was based on subjective judgement of influence.}
